Assertion Contracts

### 2022-02-17 papers/assertion-contract/paper.tex
update the code

    function validate(uint p, uint seed) 
    public view returns (uint) {
        uint range = p / 2 - 2; 
        uint r = seed % range + 2;
        uint cal = p % r;

        uint result = 0; // an non-award computational proof 
        if (cal == 0)  
            result = 2; // a counterexample
        else 
            {
                uint result_target = 
                    uint (keccak256(abi.encodePacked(seed, cal)));
                if (result_target <= target) 
                    result = 1; // a computational proof    
            }
        return result;           
    }
}

@@

    function validate(uint[] memory p, uint seed)
    public view returns (uint) {
        uint range_1 = p.length - 1; 
        require(range_1 > 0, "invalid range");
        uint n = seed_i % range_1 + 1;
        uint range_2 = n;
        require(range_2 > 0, "invalid range");
        uint m = seed_j % range_2 ;

        uint cal_1 = p[m];
        uint cal_2 = p[n];

        uint result = 0; // an non-award computational proof 
        if (cal_1 > cal_2)  
            result = 2; // a counterexample
        else 
            {
            uint result_target = 
                 int (keccak256(abi.encodePacked(seed, cal_1, cal_2)));
            if (result_target <= target) 
                result = 1; // a computational proof      
        }             
        return result;           
    }
}

@@

    function validate(uint[10] memory p, uint seed) 
    public view returns (uint) {
        uint range = p.length; 
        uint k = seed % range + 1;

        uint cal_1 = p[k];
        uint cal_2 = p[(k - 1) / 2];

        uint result = 0; // an non-award computational proof 
        if (cal_1 < cal_2)  
            result = 2; // a counterexample
        else {
            uint result_target = 
                uint (keccak256(abi.encodePacked(seed, cal_1, cal_2)));
            if (result_target <= target) 
                result = 1; // a computational proof      
        }              
        return result;           
    }
}

@@

        uint result = 0; // an non-award computational proof 
        if ((cal_1 == 0) && (cal_2 == 0))  
            result = 2; // a counterexample
        else {
            uint result_target = 
                uint (keccak256(abi.encodePacked(seed, cal_1, cal_2)));
            if (result_target <= target) 
                result = 1; // a computational proof      
        }              
        return result;           
    }
}

>>>>

    function validate(uint a, uint seed) 
    public view returns (uint) {
        uint range = a / 2 - 2; 
        uint r = seed % range + 2;
        uint cal = a % r;
        bool p = (cal == 0);

        uint result = 0; // an non-award computational proof 
        if (p)  
            result = 2; // a counterexample
        else 
            {
                uint result_target = 
                    uint (keccak256(abi.encodePacked(seed, cal)));
                if (result_target <= target) 
                    result = 1; // a computational proof    
            }
        return result;           
    }
}

@@

    function validate(uint[] memory a, uint seed)
    public view returns (uint) {
        uint range_1 = a.length - 1; 
        require(range_1 > 0, "invalid range");
        uint n = seed % range_1 + 1;
        uint range_2 = n;
        require(range_2 > 0, "invalid range");
        uint seed_1 = uint (keccak256(abi.encodePacked(seed, n)));
        uint m = seed_1 % range_2 ;

        uint cal_1 = a[m];
        uint cal_2 = a[n];

        bool p = (cal_1 > cal_2);

        uint result = 0; // an non-award computational proof 
        if (p)  
            result = 2; // a counterexample
        else 
            {
            uint result_target = 
                uint (keccak256(abi.encodePacked(seed, cal_1, cal_2)));
            if (result_target <= target) 
                result = 1; // a computational proof      
        }             
        return result;           
    }
}

@@

    function validate(uint[10] memory a, uint seed) 
    public view returns (uint) {
        uint range = a.length; 
        uint k = seed % range + 1;

        uint cal_1 = a[k];
        uint cal_2 = a[(k - 1) / 2];

        bool p = (cal_1 < cal_2);

        uint result = 0; // an non-award computational proof 
        if (p)  
            result = 2; // a counterexample
        else {
            uint result_target = 
                uint (keccak256(abi.encodePacked(seed, cal_1, cal_2)));
            if (result_target <= target) 
                result = 1; // a computational proof      
        }              
        return result;           
    }
}

@@

        bool p = (cal_1 == 0) && (cal_2 == 0);

        uint result = 0; // an non-award computational proof 
        if (p)  
            result = 2; // a counterexample
        else {
            uint result_target = 
                uint (keccak256(abi.encodePacked(seed, cal_1, cal_2)));
            if (result_target <= target) 
                result = 1; // a computational proof      
        }              
        return result;           
    }
}
